Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-06 ms.tex
10th time through intro

Knowledge of how $\dot{M}$ depends on the SMBH mass, $\Mbh$, and other
properties of the galactic nucleus informs key questions related to
the co-evolution of SMBHs and their host galaxies with cosmic time
(e.g.~\citealt{Kormendy&Ho13}; \citealt{Heckman&Best14}).  SMBH growth
in the low redshift universe is dominated by low mass black holes,
$M_{\bullet} \lesssim 10^{8}M_{\odot}$ (e.g.~\citealt{Heckman+04}), a
fact which is often attributed to the general trend of `cosmic
down-sizing' resulting from hierarchical structure growth (e.g,
\citealt{Gallo+08}).  However, the physical processes involved in the
growth of low mass blacks may be distinct from those operating at
higher SMBH masses and accretion rates in quasars.  A key question
here is whether SMBHs grow primarily by accreting gas fed in directly
from large scales, or whether significant growth results also from
internal, secular processes such as local stellar mass loss.

Obtaining a better undersatnding of the physical mechanisms
responsible for accretion onto quiescent SMBHs would have implications
for observational constraints on the occupation fraction of SMBHs in
low mass galaxies, and the potential existence of intermediate mass
black holes.  \citet{Miller+15} combine the average correlation
between $\Mbh$ and the nuclear X-ray luminosities, $L_{X}$ of a sample
of elliptical galaxies to infer tentative evidence for a SMBH
occupation fraction less than unity in galaxies with stellar masses
$M_{\star} \lesssim 10^{10}M_{\odot}$ ($M_{\bullet} \lesssim
10^{7}M_{\odot}$).  This method relies on extrapolating a power-law
fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below
the detection threshold, despite the potential that rather different
physical processes control the accretion rates onto the lowest mass
SMBHs.

>>>>

Knowledge of how $\dot{M}$ depends on the SMBH mass, $\Mbh$, and other
properties of the galactic nucleus informs key questions related to
the co-evolution of SMBHs and their host galaxies with cosmic time
(e.g.~\citealt{Kormendy&Ho13}; \citealt{Heckman&Best14}).  SMBH growth
in the low redshift universe is dominated by low mass black holes,
$M_{\bullet} \lesssim 10^{8}M_{\odot}$ (e.g.~\citealt{Heckman+04}), a
fact which is often attributed to the general trend of `cosmic
down-sizing' resulting from hierarchical structure growth (e.g,
\citealt{Gallo+08}).  However, the physical processes involved in the
growth of low mass blacks may be distinct from those operating at
higher SMBH masses and accretion rates in quasars.  A key question
here is whether SMBHs grow primarily by accreting gas fed in directly
from large scales (galactic or extra-galactic), or whether significant growth results also from
internal, secular processes such as local stellar mass loss in the nuclear region.

Obtaining a better understanding of the mechanisms regulating accretion onto quiescent SMBHs would have implications
for a variety of observats, including constraints on the occupation fraction of SMBHs in
low mass galaxies, and the potential existence of intermediate mass
black holes.  \citet{Miller+15} use the average correlation
between $\Mbh$ and the nuclear X-ray luminosities, $L_{X}$, of a sample
of elliptical galaxies to infer tentative evidence for a SMBH
occupation fraction less than unity in galaxies with stellar masses
$M_{\star} \lesssim 10^{10}M_{\odot}$ ($M_{\bullet} \lesssim
10^{7}M_{\odot}$).  This method relies on extrapolating a power-law
fit of the $L_X-\Mbh$ distribution to low values of $L_{\rm X}$ below
the detection threshold, a potentially worrisome assumption if different
physical processes control the accretion rates onto the lowest mass
SMBHs.
